Comparison of Two Second Order Traffic Flow Models

### 2015-03-11 Presentation/presentation.tex
More edits to presentation

@@

\hspace{2em} ``A fluid particle responds to stimuli from the front and from \\ 
\hspace{2em} behind, but a car is an anisotropic particle that mostly \\
\hspace{2em} responds to frontal stimuli." CITATION

@@

\[ \left\{ \begin{matrix*}[l] \rho_t + (\rho v)_x = 0 \\[2ex] (v + \rho)_t + v(v + \rho)_x = 0 \end{matrix*} \right. \]

@@

Conserved quantities:
\begin{enumerate}
\item Mass (density): $\rho$
\item ``Momentum": $y = v + p(\rho)$
\end{enumerate}

@@

Aw and Rascle (2000) propose some conditions for traffic models:
\begin{enumerate}
\item The system must be hyperbolic.
\item When solving the Riemann problem with bounded nonnegative data $(\rho, v)$, the density and velocity must remain nonnegative and bounded from above.
\item When solving the Riemann problem with data $Q_{\pm} = (\rho_{\pm}, v_{\pm})$, all waves connecting any state $Q = (\rho, v)$ to its left (behind it) must have a propagation speed (eigenvalue or shock speed) at most equal to the velocity $v$.  
\item The solution to the Riemann problem must agree with the qualitative properties that each driver practically observes every day.
\item Near the vacuum, the solution to the Riemann problem must be very sensitive to the data (no continuous dependence with respect to initial data at $\rho = 0$). 
\end{enumerate}

>>>>

\begin{frame}
\frametitle{Introduction}
\hspace{4.75em} First and second order traffic flow models: \\[3ex]

\[ \begin{matrix*}[l]
\text{LWR: } & \rho_t + \Big(\rho V(\rho)\Big)_x = 0 \\[4ex]

\text{PW: } & \left\{ \begin{matrix*}[l] \rho_t + (\rho v)_x = 0 \\[1ex] v_t + v v_x + \dfrac{p'(\rho)}{\rho} \rho_x = \dfrac{V(\rho) - v}{\tau} + \mu v_{xx} \end{matrix*} \right. \\[6ex]

\text{AR: } &  \left\{ \begin{matrix*}[l] \rho_t + (\rho v)_x = 0 \\[1ex] v_t + \Big( v - \rho p'(\rho) \Big)_x = 0 \end{matrix*} \right.
\end{matrix*} \]

@@

\hspace{2em} ``A fluid particle responds to stimuli from the front and from \\ 
\hspace{2em} behind, but a car is an anisotropic particle that mostly \\
\hspace{2em} responds to frontal stimuli." \cite{Daganzo1995}

@@

\[ \left\{ \begin{matrix*}[l] \rho_t + (\rho v)_x = 0 \\[2ex] \Big(v + p(\rho)\Big)_t + v\Big(v + p(\rho)\Big)_x = 0 \end{matrix*} \right. \]

@@

Conserved quantities:
\begin{enumerate}
\item Mass (density): $\rho$
\item ``Momentum": $y = \rho(v + p(\rho))$
\end{enumerate}

@@

Aw and Rascle propose some conditions for traffic models \cite{AwRascle2000}:
\begin{enumerate}
\item When solving the Riemann problem, the density and velocity must remain nonnegative and bounded from above.
\item When solving the Riemann problem, all waves connecting any state $Q = (\rho, v)$ to its left (behind it) must have a propagation speed (eigenvalue or shock speed) at most equal to the velocity $v$.  
\item The solution to the Riemann problem must agree with the qualitative properties that each driver practically observes every day.
\end{enumerate}
